ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
4th topic

    \topic{odgi break, groom, chop \& unchop} \odgi\ allows edit operations on the graphs. Cycles in the graph
    complicate downstream analyses: \cmd{odgi break} removes the cycles, reducing the complexity of the graph topology.
    \cmd{odgi groom} removes spurious inverting links by exploring the graph from the orientation supported by most
    paths. To enable efficient sequence alignment against the graph, long nodes can be divided into shorter nodes
    at a maximum requested size using \cmd{odgi chop}. Partial order alignment, which consists of aligning sequences
    against a directed acyclic graph (DAG), is frequently used in pangenome building pipelines, but the current
    implementations return DAGs with 1-bp long nodes; \cmd{odgi unchop} allows joining nodes that can be merged
    without changing the graph topology, nor the embedded sequences, obtaining an equivalent, but more compact,
    representation of the graph.

>>>>

    \topic{odgi break, groom, chop \& unchop} \odgi\ pangenome graphs are dynamic structures in \odgi\.
    \cmd{odgi break} removes cycles in the graph, reducing its topology complexity. \cmd{odgi groom}
    removes spurious inverting links by exploring the graph from the orientation supported by most paths. \cmd{odgi chop}
    divides long nodes into shorter ones at a maximum requested size, simplifying downstream analysis.
    \cmd{odgi unchop} allows joining nodes that can be merged without changing the graph topology, nor the
    embedded sequences, obtaining an equivalent, but more compact, representation of the graph.
